The Role of Ice Compositions and Morphology for Snowlines and the C/N/O Ratios in Active Disks

### 2016-03-07 tex/draft2/ms_edited.tex
update

\begin{figure}[h!]
\centering
\includegraphics[width=0.5\textwidth]{C_O_water_ice.pdf}
%\vspace{-0.5in}
\caption{C/O ratio estimates in gas (solid lines) and dust (dashed lines) as function of semimajor axis in a viscous disk, for CO as water dominated ices (top panel) or as pure ice (bottom panel). The H$_2$O, CO$_2$ and CO snowlines are shown for particles with initial sizes $\sim0.001$ cm $\lesssim s \lesssim$ 7 m as indicated by the color bar. The C/O ratio in a static disk (black lines) is shown for comparison. The arrows show that the C/O ratio in gas will decrease inside the H$_2$O and CO$_2$
snowlines in the viscous disk, as the relative fluxes of the desorbed icy
particles and the overall nebular gas will cause an excess of oxygen gas inside these snowlines (see Paper I for details). The presence of CO in a water ice environment rather than as pure ice moves the CO snowline significantly inward by $\sim$70\%. Taken together, disk dynamics and ice morphology move the CO snowline inward by a factor of $\sim$7.} 
\label{fig:CO_ratio}
\end{figure}

@@

\begin{figure}[h!]
\centering
\includegraphics[width=0.5\textwidth]{N_O_water_ice.pdf}
%\vspace{-0.5in}
\caption{N/O ratio estimates in gas (solid lines) and dust (dashed lines) as function of semimajor axis in a viscous disk, for CO and N$_2$ as water dominated ices (top panel) or as pure ices (bottom panel). The H$_2$O, CO$_2$, CO and N$_2$ snowlines are shown for particles with initial sizes $\sim0.001$ cm $\lesssim s \lesssim$ 7 m as indicated by the color bar. The N/O ratio in a static disk (black lines) is shown for comparison. The arrows show that the N/O ratio in gas will decrease inside the H$_2$O and CO$_2$ snowlines in the viscous disk, as the relative fluxes of the desorbed icy
particles and the overall nebular gas will cause an excess of oxygen gas inside these snowlines (see Paper I for details). Radial drift and gas accretion move the N$_2$ snowline inward by up to $\sim$50\% compared to a static disk. The presence of N$_2$ in a water ice environment rather than as pure ice moves the N$_2$ snowline significantly inward by $\sim$70\%. Taken together, disk dynamics and ice morphology move the CO snowline inward by a factor of $\sim$7. The results of highly enhanced gas-phase N/O ratios between the CO$_2$ and CO snowlines compared to its average value, and of highly elevated N/O ratios in gas between the CO and N$_2$ snowlines (see Figure \ref{fig:Nstatic}), are preserved.}  
\label{fig:NO_ratio}
\end{figure}

>>>>

\begin{figure}[h!]
\centering
\includegraphics[width=0.5\textwidth]{C_O_water_ice.pdf}
%\vspace{-0.5in}
\caption{C/O ratio estimates in gas (solid lines) and dust (dashed lines) as function of semimajor axis in a viscous disk, for CO as pure ice (top panel) or as water dominated ices (bottom panel). The H$_2$O, CO$_2$ and CO snowlines are shown for particles with initial sizes $\sim0.001$ cm $\lesssim s \lesssim$ 7 m as indicated by the color bar. The C/O ratio in a static disk (black lines) is shown for comparison. The arrows show that the C/O ratio in gas will decrease inside the H$_2$O and CO$_2$
snowlines in the viscous disk, as the relative fluxes of the desorbed icy
particles and the overall nebular gas will cause an excess of oxygen gas inside these snowlines (see Paper I for details). The presence of CO in a water ice environment rather than as pure ice moves the CO snowline significantly inward by $\sim$70\%. Taken together, disk dynamics and ice morphology move the CO snowline inward by a factor of $\sim$7.} 
\label{fig:CO_ratio}
\end{figure}

@@

\begin{figure}[h!]
\centering
\includegraphics[width=0.5\textwidth]{N_O_water_ice.pdf}
%\vspace{-0.5in}
\caption{N/O ratio estimates in gas (solid lines) and dust (dashed lines) as function of semimajor axis in a viscous disk, for CO and N$_2$ as pure ices (top panel) or as water dominated ices (bottom panel). The H$_2$O, CO$_2$ and N$_2$ snowlines are shown for particles with initial sizes $\sim0.001$ cm $\lesssim s \lesssim$ 7 m as indicated by the color bar. The CO snowline (inner vertical dashed line in both panels) is only shown for the 7 m particles. The N/O ratio in a static disk (black lines) is shown for comparison. The downward arrows show that the N/O ratio in gas will decrease inside the H$_2$O and CO$_2$ snowlines in the viscous disk, as the relative fluxes of the desorbed icy
particles and the overall nebular gas will cause an excess of oxygen gas inside these snowlines (see Paper I for details). Radial drift and gas accretion move the N$_2$ snowline inward by up to $\sim$50\% compared to a static disk. The presence of N$_2$ in a water ice environment rather than as pure ice moves the N$_2$ snowline significantly inward by $\sim$70\%. Taken together, disk dynamics and ice morphology move the CO snowline inward by a factor of $\sim$7. The results of highly enhanced gas-phase N/O ratios between the CO$_2$ and CO snowlines compared to its average value, and of highly elevated N/O ratios in gas between the CO and N$_2$ snowlines (see Figure \ref{fig:Nstatic}), are preserved.}  
\label{fig:NO_ratio}
\end{figure}
